\article{Student \change[S]{Representation}{Delegates}}

The USG shall designate the \change[P]{Undergraduate Student Representatives (USRs)}{\protect\acp{USD}} in all official matters and University Committees. The USDs \change[S]{bring the perspective of Undergraduate Students}{present the USB's perspective and interests} to the Academic Board as laid out in the Academic Constitution of Jacobs University Bremen. 

\section{University Committees with Undergraduate Student Representation}
The Committees in the \hyperref[USGexecutiveUnitDef]{USG Executive Unit} carry the task of delegating students to the following University Committees with Undergraduate Student Delegates. These USDs are mandated to join the respective University Committee. \add[S]{The USD's don't need to be members of the respective USG executive committee. }In particular,
\begin{enumerate}
\item the Academic Affairs Committee is responsible for \change[S]{delegating students to}{selecting delegates (and substitutes) for} the:
\begin{enumerate}
    \item Academic Senate (AS),
    \item \change[S]{University Education Committee (UEC),}{University Committee on Education (UCE),}
    \item \change[S]{Quality Management (QM) Team}{University Committee on Quality management (UCQM)},\add[S]{
    \protect\item University Committee on Academic Integrity (UCAI),}
    \item Teacher of the Year Delegates,
    \item Hiring Committees;
\end{enumerate}
\item the Campus Affairs Committee is responsible for \change[S]{delegating students to}{selecting delegates for} the:
\begin{enumerate}
    \item Equality Committee (EQ),
    \item Disciplinary Counsel (DC).
\end{enumerate}
\end{enumerate}
\add[S]{Only in exceptional cases, as decided by the \protect\hyperref[USGParliamentDef]{USG Parliament}, a student is allowed to be the Undergraduate Student Delegate (excluding substitutes) of more than one University Committee of Jacobs University.}

\section{Decision-Making}
The USDs shall be free to vote in the \add[P]{University} Committees as their consciousness dictates. The Student Parliament \add[S]{or the responsible Committee }may however dictate the USDs' votes in their \add[P]{University} Committees, \change[S]{if a two-thirds (2/3) majority of the Members of Parliament or respective USG Executive Committee decides so}{by a simple 2/3 majority vote}. If unable to attend the official meetings, the USD is responsible for finding a substitute.

\section{Tasks of the Undergraduate Student Delegates}
The Undergraduate Student Delegates shall:
\begin{enumerate}
    \item attend all meetings of their \change[S]{delegated University Committee}{University Committee},
    \item \change[S]{attend all meetings of the responsible USG Executive Committee}{attend all meeting of the responsible USG Executive Committee, when decided so by the respective Committee}\note[Colin]{Not necessary for instance of the UCAI USDs},
    \item upon decision by the Parliament, additionally attend all meetings of the USG Parliament (as is the case for the USD in the Academic Senate),
    \item present a summary of the \add[S]{work of the }University Committee to the \change[S]{USG in the responsible Executive Committee and/or the Parliament}{responsible Executive Committee and/or the Parliament}, after each University Committee meeting or whenever asked to do so,
    \item at their discretion, or when mandated by the responsible USG Committee or the Parliament, invite other students as guests to the University Committee meeting.
\end{enumerate}