\add[S]{
\protect\article{Elections}
\section{Elections}
\label{electiontimes}
The USG shall hold a general election twice a year, in particular:
\begin{enumerate}
	\item in first week of December for: \remove[RS]{Vice-President, }Focus Area representatives, Treasurer\add[S]{, 5 Members of Parliament } (and for any open position),
	\item in first week of May for: \remove[RS]{President, }College representatives\add[S]{, 5 Members of Parliament} (and for any open position).
\end{enumerate}

\add[S]{\protect\section{Candidates Eligibility}\protect\label{sect:eligible}
	The student shall be physically present in the respective semester of being in the office.
	\begin{parenum}
		\item Students in their second year of study who will spend the fifth semester abroad or will do an internship in their fifth semester may not run for an office in the USG in the May elections of their second year.	
		\item Students in their third year of study may not run as Focus area or College representatives in the May elections of their last year.
		\item Foundation Year students can run and vote for the representative of their college. In case, they have been offered admission for undergraduate studies and accepted that offer, they may also vote for the Focus area representative of their future Focus area.
	\end{parenum}
}

\add[S]{
	\protect\section{Election of the Members of Parliament}
	\add[S]{Only active members of an USG Executive Committee are eligible to run as a Member of Parliament. }
	For the election of the Member of Parliament, each student may distribute three (3) votes on candidates. Then, the Members of Parliament are selected based on the outcome of the election as follows:  
	\protect\begin{parenum}
		\item Firstly, the candidates with most votes (except for a number of candidates equal to the number of executive Committees) become Member of Parliament. 
		%Firstly, the $5-n$ candidates with most votes (where $n$ denotes the number of executive Committees of the USG) become Member of Parliament. For each Parliament position to be refilled (due ot resignations of impeachments) one additional candidate is elected by a majority vote.
		\item All remaining positions are filled by the candidate reaching most votes from every Committee, which isn't already chosen as a Member of Parliament in \textbf{\S1}.
	\end{parenum}
}

\add[S]{
	\protect\section{Election of the College and Focus area representatives}
	Any eligible student according to section \ref{sect:eligible} student may run as a college or Focus area representative in their College or Focus area. Focus area and College representatives are elected by the USB from within their Focus area or College.
}

\add[S]{
	\protect\section{Election of the President's office}
	\label{PresiElection}
	In the beginning of each Fall semester, the newly elected Parliament shall elect a President and in the beginning of each Spring semester they shall elect a Vice-President amongst the Members of Parliament. Both President and Vice-President can be recalled any time with an absolute 2/3 majority in the Parliament. In this case, a new President must be elected immediately.
}

\section{Term Length}
By default, all elected positions' terms within the USG shall be one year long.
\begin{parenum}
	\item Exceptions of the above, with one-semester terms, are:
	\begin{enumerate}
		\item 
		the candidates are third year students elected in the December election of their third year, and they are graduating at the end of their 6\textsuperscript{th} semester,
		\item 
		the candidates are second year students elected in the December election of their second year, and they are going abroad during their 5\textsuperscript{th} semester,
		\item
		the candidates are running for an open position from a previous one-semester term,
		\item
		the candidates receive the second highest number of votes in an election where two positions are to be filled,
		\item
		the candidates receive the second highest number of votes in an election where any Member of Parliament runs and is elected for a different position within the Parliament,
		\item
		elected members choose to have a one semester term.
	\end{enumerate}
	\item
	The current members at the time of the election will remain in office until the end of the respective semester. After the elections, the newly elected members are already invited as standing guests in the meetings. They obtain voting power already at the beginning of the respective break (winter or summer break). In particular, this means that for the breaks between semesters, both previous and newly-elect students are members of the Parliament and thus have voting rights.
	\item
	A student can run for a position as many times as they wish.
	
\end{parenum}
}