\article{Financial Affairs Committee By-Laws}

\label{FinByLawsdef}
\section{General Responsibilities of the Committee}
The Financial Affairs Committee (FAC) of the Undergraduate Student Government (USG) shall manage the USG Budget. The USG and FAC shall, with their available funds, endeavor to financially support public, non-profit events, initiatives and the like of students, which are to the potential benefit of the student body as a whole. These include events on campus, competitions attended by a delegation of the student body, student-led projects and student-led excursions. These are only examples; general rules are that the initiative shall:
\begin{enumerate}
\item	not be exclusive but potentially open to any student to attend or be a part of, 
\item	be carried out to the advancement of the student body and the benefit in improving student life in academic, socio-cultural or other aspects,
\item	not be harmful to Jacobs University's image or reputation.
\end{enumerate}

The Chair of the FAC shall have direct contact with the Campus Life Department regarding the undergraduate students' funds and the USG Budget.


\section{Tasks}
The fixed and recurring tasks of the FAC shall be: 
\begin{enumerate}
\item to convene weekly in meetings chaired by the Treasurer,
\item the evaluation of Funding Applications or Addenda,
\item the approval or rejection of a Funding Application or an Addendum
\item the writing of confidential, USG-internal reports on why respective Funding Applications or Addenda were approved or rejected, containing specific recommendations for the USG Parliament,
\item the submission of approved Funding Applications and Addenda as well as the corresponding reports to the USG Parliament,
\item the checking and approval of receipts and invoices and their submission of such receipts and invoices to the Campus Life Department,
\item the accounting of the USG Budget and notification of the USG Parliament about the situation of the USG Budget,
\item communication to the respective staff within the administrative body of Jacobs University.
\end{enumerate}


\section{Duties of the Treasurer}
The FAC shall be led by an USG Parliamentarian who has been directly elected in the position of ``Treasurer'' by the student body. The Treasurer takes the reponsibility for:

\begin{enumerate}
\item all work of and within the Financial Affairs Committee,
\item attendance of all USG Parliament meetings and presentation of current FAC matters,
\item communication with the USG such as recommendations or reports on Funding Applications,
\item the submission of an annual budget report at the end of each academic year to the USG Parliament,
\item passing on all relevant information to the succeeding Treasurer,
\item the establishment of the FAC as defined in Article \ref{FinByLawsdef}, Section \ref{fin:establishment}.
\end{enumerate}

\sectionss{Establishment of the FAC}\label{fin:establishment}
\begin{parenum}
\item The Treasurer shall conduct a formal application procedure in conjunction with a second USG Parliamentarian for students wishing to join the FAC.
\item The size of the FAC for effective and efficient functioning shall be decided by the Treasurer. 
\item Committee members of the FAC shall hereafter be referred to as ``Financial Experts''.
\end{parenum}

\section{Student's Right to Apply for Funding}
All students of Jacobs University shall have the right to apply for funding of the USG for their initiatives and/or club activities, as long as the criteria specified in these By-Laws are met.

{\add[P]{\protect\section{Funding Applications}
All Applications have to go through the FAC first, and the FAC has the right to decline any incoming application.

The FAC has the authority to fund  Applications or Addenda that amount up to $\euro$500 and the obligation to emit a formal notification about such funding to the USG Parliament. This shall be valid only if the FAC consists of more than seven (7)  members.

Any amount exceeding $\euro$500 will require an additional approval by the President's office, and any amount exceeding $\euro$1000 will require vote of approval by a simple majority in the USG Parliament.}

\section{Profit-Generating Events}
The FAC shall only fund profit-generating events, initiatives, and the like as long as they meet one of the following criteria:
\begin{enumerate}
  \item profits are reinvested in the continuity of the club or event,
	\item profits are donated to a cause deemed appropriate by the Parliamentary Finance Committee if the Funding Application is $\euro$250 or less, and by the Undergraduate Student Government if the application exceeds $\euro$500,
	\item profits are returned to the USG Budget.
\end{enumerate}

\sectionss{Miscellaneous Funding Regulation}
\begin{parenum}
% SPECIFIC: REDISTRIBUTION (not to be in this document)
\item The FAC has the authority to approve or reject Addenda for redistribution of funds, as long as they remain in the limit of the initial budget. Addenda intent on raising the initial budget stipulated in the initial Funding Applications can only be approved by the FAC if they request up to $\euro$200, as otherwise they have to be approved by the USG Parliament. 
%% CAN BE ABUSED. WISH OF FAC ON OCTOBER 9TH TO HAVE: ADDENDUMS ONLY FOR REALLOCATION, IF INCREASE, THEN NEW APPLICATION SHOULD BE SUBMITTED\\
% SPECIFIC: LOGO FOR ORGANIZATIONS (requirement not there yet in any previous section!!!)
\item The FAC has the authority to waive the requirement according to which the organizers are obliged to portray the USG logo in certain events or clubs.
% SPECIFIC: LENDING PROPERTY ?!
\item The FAC has the authority to lend out USG property with reasonable assurance of return. The Chair is responsible for the management of property loans. If the Chair shall be indisposed for an extended period of time, the USG Parliament can opt for ceding this power to the USG President for the duration of the Chair's absence if the Chair has provided a signed temporary removal of power.
\end{parenum}