\article{President's Office}
\label{PresByLawsDef}
\section{General Responsibilities of the President's Office}
The President's Office and its Support Structures shall convene and preside weekly meetings of the USG Parliament. The President's Office shall oversee the workings of the committees of the USG, taking the information and their opinions into account when making decisions.

\section{Duties of the President}
\label{PresDef}
The President shall act as the primary representative of the USG to the \hyperref[studentbody]{USB}, and the primary representative of the USB to the University Administration.
The President shall ensure the proper functioning and efficiency of the Committees of the USG.

%%% TODO EXTERNAL POWER

\section{Duties of the Vice President}
\label{VPDef}
The Vice President shall aid the President in any matters pertaining to the duties of the President to the best interest of the USG. The Vice President shall further:
\begin{enumerate}
\item \label{VPdeputy} be the Acting Head of the USG whenever the President is absent and/or not legitimized,
\item oversee the matters of the Disciplinary Council and attend the hearings when they occur,
\item be the foremost contact for further developing and advancing the disciplinary procedures at Jacobs University together with its administration.
\end{enumerate}


\section{Event of Untimely Termination}
In the event that the President/Vice-President steps down from his/her role before the proper conclusion of the term, a new President shall be elected from the existing members of the \hyperref[USGParliamentDef]{USG Parliament} in the earliest possible convenience. 
\begin{parenum}
\item In accordance with Article \ref{PresByLawsDef}, Section \ref{VPDef}, Point \ref{VPdeputy}, the Vice President shall become the Interim President of the USG until the proper introduction of the new President into his/her office.
\item There shall be no role of interim Vice President until the conclusion of the said election. 
\end{parenum}