%% TODO CHANGE: EAP DELEGATE IS CHAIR BY DEFAULT, BUT COMMITTEE CAN CHANGE THAT
%% MAYBE: CHAIR IS DELEGATE EVERYWHERE BY DEFAULT, NEEDS TO FIND REPS FROM COMMITEE
\article{Academic Affairs Committee By-Laws}
\label{AACByLawsdef}
\section{General Responsibilities of the Committee}
The Academic Affairs Committee (AAC) of the Undergraduate Student Government (\hyperref[USGdef]{USG}) shall gather undergraduate student opinions on current academic issues and represent and mediate the students' opinions towards faculty and staff. 

\begin{parenum}
\item The Committee shall strive for the best solution for the \hyperref[studentbody]{USB} as a whole. It is the objective of the committee to enhance overall teaching quality.
\item The Committee shall be the contact institution for students who have problems with or suggestions about academic policies and regulations. The committee shall maintain an open mind and look for solutions and new ideas within the academic realm at Jacobs University.
\end{parenum}

\add[P]{\protect\section{Composition and Roles}
The AAC shall be represented by students of all focus areas, and all majors.
Each focus area shall elect its representative, who is a member of the Parliament as well. Students may become members of the AAC representing their majors.
Special roles within the AAC are, but not limited to:}
\protect\begin{enumerate}
    \item \add[P]{AAC Chair}\add[S]{
    \protect\item Focus area representatives}\add[P]{
    \protect\item Undergraduate Student Representative}\add[S]{(and substitute)}\add[P]{ in the Academic Senate}\add[S]{
    \protect\item Undergraduate Student Representatives (and substitutes) in the University Committee on Education
    \protect\item Undergraduate Student Representative (and substitute) in the University Committee on Quality Management
    \protect\item Undergraduate Student Representatives (and substitutes) in the University Committee on Academic Integrity}\add[P]{
    \protect\item Hiring Committees Ombudsperson
    \protect\item AAC Secretary
    \protect\item USR for Awards Committees, such as the Teacher of the Year and Lecture Hall Awards.}
\end{enumerate}

\add[S]{
\protect\section{Major Representatives}
In order to better represents the interest of students of all major's on campus, the AAC selects major representatives among the \acl{USB} for undergraduate study programs. Ideally, there should be one to two major representatives for each major, especially if there are no AAC members of that major. %to support inform about and advise the AAC on issues and tasks relevant specifically to their major.
Major representatives don't need to be AAC members. Major representatives shall:\begin{enumerate}
	\item serve as a point of contact for students of their major,
	\item address major specific issues autonomously, wherever possible,
	\item advise the AAC on matters related to their major,
	\item collect feedback and complaints from students of their major and either address them themselves or present them to and collaborate with the AAC in order to address them.
\end{enumerate}
}

\add[S]{
	\protect\section{Focus area representatives}
	The elected Focus area representatives shall become AAC members. The Focus area representatives shall:
	\begin{enumerate}
		\item serve as a point of contact for students and major-representatives of their focus area,
		\item work on issues specific to their focus area,
		\item represent the interest of their Focus area in AAC internal discussions, thus ensuring the needs of all Focus areas are taken into account,
		\item stay in contact with and support the work of the major representatives of their focus area, serving as a link between the major representatives and the AAC.
	\end{enumerate}
}

\add[P]{\protect\section{Tasks}
The Committee shall work on relevant suggestions and requests from individual students or other institutions. The fixed and recurrent tasks of the committee shall pertain to:}

\protect\begin{enumerate}
\item \add[P]{give feedback about academic matters to faculty, administration and the respective }\add[S]{university}\add[P]{Committees (}\add[S]{primarily the }\change[S]{Quality Management, }{University Committee on Quality Management and }\change[S]{University Education Committee/Education Advisory Panel}{University Committee on Education}),\add[P]{
\protect\item regularly update the \protect\hyperref[studentbody]{USB} and the Parliament about its workings as well as the meetings with the university leadership and the Academic University Committees,
\protect\item be responsible for meeting with the University Leadership of Academic Operations at least once per semester, to discuss academic developments,}
\protect\item \change[S]{represent the \protect\hyperref[studentbody]{USB}'s concerns and opinions in any relevant internal discussions,}{represent the USB's interest in the University Committees,}\add[P]{
\protect\item structure changes and their implications, evaluate academic policies,major evaluations.}
\end{enumerate}

\remove[RS]{\protect\section{Duties of the Chair}
The AAC chair shall become the undergraduate student representative and a member to the UEC for the respective academic year. The chair shall attend all UEC meetings. It is at the discretion of the chair to invite additional members of the AAC to attend UEC meetings.}