\article{Final provisions and policy changes}\label{art:final}

\section{Constitution Scope}
The constitution of the \hyperref[studentbody]{USB} at Jacobs University is of a general character. Any foregoing article of the constitution may be complemented, according to this constitution, with provisions issued by the USG.
\begin{parenum}
\item \hyperref[PartA]{Part A} of this document\add[S]{ and the articles \protect\ref{art:judicative} and \protect\ref{art:final}} \change[S]{is}{forms} the \remove[S]{explicit }Constitution, \change[S]{that}{which} has to be amended according to Article \protect\ref{art:final}, Section \protect\ref{Ammendments}.
\item \add[S]{\protect\hyperref[PartB]{Part B} represents By-Laws and secondary provisions, \change[S]{that}{which} can be changed internally by the \protect\hyperref[USGParliamentDef]{USG Parliament} according to Article \protect\ref{art:final}, Section \protect\ref{sec:internal-changes}}
\item \add[S]{\protect\hyperref[PartC]{Part C} represents complementary provisions, definitions and guidelines.}
\end{parenum}

\section{Amendments and Referendum}
\label{Ammendments}
Amendments of this constitution or the ratification of a new constitution can only be passed in a successful referendum by the \hyperref[studentbody]{USB}. Before the organization of a referendum, any new constitution or amendments to the old constitution must be introduced via a general assembly to the \hyperref[studentbody]{USB}. 

\section{Overruling} 
The provisions of this constitution shall not violate in any way general provisions of German, European, or international law as far as applicable. If such provisions exist, they shall be immediately revoked and/or amended.

\sectionss{Internal Changes and Amendments of By-Laws}\label{sec:internal-changes}
\begin{parenum}
\item Existing by-laws and provisions can be amended or replaced and new ones can be introduced only with a two-thirds (2/3) majority of members voting in favour.
\item If the name of a document, Committee, unit, or office mentioned in this constitution changes without the change of the respective entity violating this constitution, this document may be updated by substitutions of the old name with the new name upon approval of the USG by a simple majority vote.
\end{parenum}

\section{Announcing changes}
If additional provisions are issued in form of complementary by-laws, the publicly available text of this constitution must clearly mention the names and articles of the relevant by-laws.


\section{Termination}
This constitution shall expire upon ratification of a new constitution by the \hyperref[studentbody]{USB}.


\vfill
\nolinenumbers
\emph{Version 1.1 of this constitution is proposed for amendment. This document has been last edited on \today.}\\

Contact for questions and suggestions:
\begin{itemize}[nosep]
\item[--] Daniel Prelipcean <\url{d.prelipcean@jacobs-university.de}> (AAC Chair 2017-2018)
\item[--] Marco David <\url{m.david@jacobs-university.de}> (AAC Chair \add[S]{Spring }2018)
\item[--] \add[S]{Colin Rothgang }<\url{colin.rothgang@jacobs-university-usg.de}>\add[S]{ (AAC Chair Fall 2018)}
\end{itemize}